Turbulence in compact to giant HII regions

### 2022-02-26 strucfunc_paper.tex
Simplify the basic strucfunc equation by using 2^x

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
 \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
 \end{enumerate}
An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.

@@

Two observational effects can modify the observed structure function at the smallest scales.
On the one hand, the blurring of the observed image by atmospheric seeing
tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile.\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
}
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
Note that the effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 s_0\).

>>>>

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = 2^{- \left( r/r_0 \right)^m} 
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
 \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
 \end{enumerate}
An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.

@@

Two observational effects can modify the observed structure function at the smallest scales.
The first is the blurring of the observed image by atmospheric seeing
tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile.\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
}
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
Note that the effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 s_0\).

The second effect is the presence of noise in the observational measurements.
Although this affects all scales,
it is most noticeable for small separations,
where the intrinsic structure function is smallest.
If the noise is spatially uncorrelated,
then it can be represented as a constant term \(B_{\text{noise}}\).
Combining the seeing and noise effects yields the corrected
model structure function:
\begin{multline}
  \tilde{B}
  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
  = \\
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r; s_0, r_0) + B_{\text{noise}}
\label{eq:sf-corrected}
\end{multline}
